---
title: "Week 4 Assignment - Developing Data Products"
author: "Kat Downey"
date: "02/08/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## 
**Shiny Application and Reproducible Pitch**
Katrina Downey
02/08/2022

##
**Project Goal**
This peer assessed assignment has two parts.

First, you will create a shiny application and deply it on the Rstudio's servers.

Second, you will use slidify or Rstudio Presenter to prepare a reproducible pitch presentation about your application.

##
**Steps to Perform**
1. Write a shiny application with associated supporting documentation. The documentation should be thought of as whatever a user will need to get started using your application
2. Deploy the application on Rstudio's shiny server
3. Share the application link by pasting it into the provided text box
4. Share your server.R and ui.R code on github


##
**How to use the application**
Simple application where you can choose the Education rate and see the impoact on Education.

The application is running here

The data used, ui.R and Server.R are in the Github Rep Here

##
```{r model}

plot(swiss$Fertility~swiss$Examination, xlab = 'Examination', ylab = 'Fertility')
abline(lm(swiss$Fertility~swiss$Examination), 
         xlab = "Education Rate",
         ylab = "Fertility Rate",
         col = "red", lwd =2)


```

